\Huge \scshape \fontfamily{pbk}\fontsize{50}{40}\selectfont The Dark \LaTeX{} \\ \medskip \normalfont \medskip\Huge An Example of the dndbook Class

### 2024-10-30 article.tex
Added Aside/Quotation to other examples; fixed layout issues with Aside/Quotation and table styles

\begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
  The |DndSidebar| is used as a sidebar. It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.
\end{DndSidebar}

>>>>

\begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
  The |DndSidebar| is used as a sidebar. It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.

  Use the |\tocside{title}| command to create an entry in the table of contents, if you want.
\end{DndSidebar}

You can represent an attached note (for example, for notes from Bigby or Mordenkainen) using the |DndAside| environment.

\begin{DndAside}
  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
\end{DndAside}

The |DndQuotation| environment goes a little further, offering the option of comment attribution, and tilts the note at a slight angle.

\begin{DndQuotation}{The Author}
  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
\end{DndQuotation}

### 2024-10-30 example.tex
Added Aside/Quotation to other examples; fixed layout issues with Aside/Quotation and table styles

\section{Tables}

\subsection{Regular Table}
The |DndTable| colors the even rows and is set to the width of a line by default.

@@

\subsection{Alternate Table Background}

@@

\subsection{Split Tables}
Temporarily adding a column using |multicols| can
be used to achieve the effect of a split column
table.

@@

This achieves the following effect:

@@

\subsection{Long Table that Spans Pages}

@@

\subsection{Tables with Footnotes}
Surrounding one of the existing table types with a |minipage| section
allows footnotes declared in the table to appear at the end of the table,
rather than in the page footer as normal. For a regularly sized table
in the two-column layout, the following declaration can be used:

@@

\subsection{Ornamented Tables}
The |ornamentedtabular| allows tables similar to those used for spellcasters
(see over page).

>>>>

\chapter{Tables}

\section{Regular Table}
The |DndTable| colors the even rows and is set to the width of a line by default.

@@

\section{Alternate Table Background}

@@

\section{Split Tables}
Temporarily adding a column using |multicols| can
be used to achieve the effect of a split column
table.

@@

%\newcolumn
This achieves the following effect:

@@

\section{Long Table that Spans Pages}

@@

\newcolumn
\section{Tables with Footnotes}
Surrounding one of the existing table types with a |minipage| section
allows footnotes declared in the table to appear at the end of the table,
rather than in the page footer as normal. For a regularly sized table
in the two-column layout, the following declaration can be used:

@@

\section{Ornamented Tables}
The |ornamentedtabular| allows tables similar to those used for spellcasters
(see over page).

### 2024-10-30 fancy-example.tex
Added Aside/Quotation to other examples; fixed layout issues with Aside/Quotation and table styles

\section{Tables}

\subsection{Regular Table}
The |DndTable| colors the even rows and is set to the width of a line by default.

@@

\subsection{Tables with Footnotes}
Surrounding one of the existing table types with a |minipage| section
allows footnotes declared in the table to appear at the end of the table,
rather than in the page footer as normal. For a regularly sized table
in the two-column layout, the following declaration can be used:

>>>>

You can represent an attached note (for example, for notes from Bigby or Mordenkainen) using the |DndAside| environment.

\begin{DndAside}
  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
\end{DndAside}

The |DndQuotation| environment goes a little further, offering the option of comment attribution, and tilts the note at a slight angle.

\begin{DndQuotation}{The Author}
  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
\end{DndQuotation}

\chapter{Tables}

\section{Regular Table}
The |DndTable| colors the even rows and is set to the width of a line by default.

@@

\section{Tables with Footnotes}
Surrounding one of the existing table types with a |minipage| section
allows footnotes declared in the table to appear at the end of the table,
rather than in the page footer as normal. For a regularly sized table
in the two-column layout, the following declaration can be used:
